Reasoning About a Machine with Local Capabilities

### 2018-05-15 toplas/paper.tex
included acknowledgements

% \begin{acks}
% This research was supported in part by the ModuRes Sapere Aude Advanced Grant
% from The Danish Council for Independent Research for the Natural Sciences (FNU). 
% Support for an STSM was received from COST Action EUTypes (CA15123).
% Dominique Devriese holds a Postdoctoral fellowship from the Research Foundation Flanders (FWO).
% \end{acks}

>>>>

\begin{acks}
This research was supported in part by the ModuRes Sapere Aude Advanced Grant
from The Danish Council for Independent Research for the Natural Sciences (FNU). 
Support for an STSM was received from COST Action EUTypes (CA15123).
Dominique Devriese holds a Postdoctoral fellowship from the Research Foundation Flanders (FWO).
\end{acks}
